### 2017-02-12 ResearchNotes/stat_exps.tex
Coomented stats 5 and 6

>>>>

\subsection{\texttt{STAT\_005} - Total Number of Activities vs Mean of
Activities per Week}

This analysis attempts to understand if the activities of courses remain the
same as the semester goes on. So the mean of the activities per course and week
is plotted, as it is displayed in figure~\ref{fig:stat_005}. The total number
of activities is also plotted in figure~\ref{fig:stat_005}.

It is visible that, although the number of activities drops as the semester
goes on, the mean number of activities stayed relatively the same despite
varying a lot. This is due to the fact that some courses stop being active as
the semester goes on, as it will be shown in section~\ref{sec:stat_006}, but
despite that, the courses that do remain active don't register a drop of
activity as time goes on.

    \includegraphics[width=\linewidth]{../src/stat_005_results/plot}

    \caption
        [Total Number of Activities vs Mean of Activities per Week]
        {Total Number of Activities vs Mean of Activities per Week.}

    \label{fig:stat_005}
\end{figure}

\subsection{\texttt{STAT\_006} - Number of Active Courses vs Number of
Activities}
\label{sec:stat_006}

A correlation is found between the total number of activities and the number of
active courses per week. The total number of active courses in a week is
plotted as a bars chart in figure~\ref{fig:stat_006}, along with the total
number of activities.

An course ceases to be active on a given week where it no longer has activities
after that week. For example, suppose a course has activities on weeks, 0, 1,
4, and 8. Then the course is only active until week 8.

The number of activities goes down with the number of active courses, as it
would be expected. But around weeks 30 to 50, it is visible that the number of
activities significantly drops from the number of courses, as opposed to the
first weeks where the numbers are much more similar. This is +probably due to
students incising lack of interest in courses' activities as the semester goes
on, which is normal behaviour.

    \includegraphics[width=\linewidth]{../src/stat_006_results/plot}

    \caption
        [Active Courses vs Number of Activities]
        {Active Courses vs Number of Activities.}

    \label{fig:stat_006}
\end{figure}
